Convex Surrogates via Polyhedral Losses

### 2019-01-30 cvx-fin.tex
add PD lemma
meeting edits

\title{Finite Property Convex Elicitation Paper}
\coltauthor{%
 \Name{Jessie} \Email{email}\\
 \addr CU
 \AND
 \Name{Raf} \Email{email}\\
 \addr CU
 \AND
 \Name{Bo}  \Email{email}\\
 \addr MSFT
}

@@

\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
  Finally, we say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
\end{definition}

@@

\raf{Transition: wait, what about dimension?}
\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
\end{definition}

@@

\begin{corollary}
  \raf{Monotonicity: WMON}
\end{corollary}

\begin{corollary}
  \raf{reduction to 1 dimension}
\end{corollary}

\section{Application: Abstain Loss}

@@

\bibliography{diss}

@@

>>>>

\title{Convex Surrogates via Polyhedral Losses}
\coltauthor{%
 \Name{Jessie} \Email{email}\\
 \addr CU
 \AND
 \Name{Raf} \Email{email}\\
 \addr CU
 \AND
 \Name{Bo}  \Email{email}\\
 \addr MSFT
}

@@

\raf{Glue needed...}
\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
\end{definition}

\begin{definition}
  We say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
\end{definition}

@@

\raf{Transition: wait, what about dimension?}

@@

\raf{Paragraph explaining two other useful necessary conditions: WMON, and reduction to 1 dimension}

\subsection{Applications: Abstain Loss and 0-1 Loss \raf{or something}}

\begin{theorem}
  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
\end{theorem}

@@

\bibliography{diss,extra}

@@

\section{To Sort}

\begin{lemma}
  Let $f_1,\ldots,f_k$ be polyhedral convex functions from $\reals^d\to\reals$.
  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
